---
title: "Interpolation_answers"
author: "YOUR NAME HERE"
output: html_document
---

# Set up

Load the following packages:

```{r message=F, warning=F}
# read in necessary packages
library(sf)
library(sp)
library(gstat)
library(tidyverse)
```

...and the `CA_precip_sf.RDS` file and the `coterm_cty_sf.RDS` file that stores the county information for California:

```{r}
p <- readRDS("./data/")
ctys <- readRDS("./data/")

# transform ctys so that it is the same projection as p `CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")`
ca <- st_transform(, st_crs())

# select for only California, STATEFP == 06
ca <- ctys %>% filter()
```

# Q1

* Use `ggplot()` to visualize precipitation in August.  Note that to do this, you will interface with `tidyverse` and `ggplot` as I did in the exercise. 

```{r}

```

# Q2

Perform Inverse Distance Weighting interpolation on your August precipitation data using a grid with `n = 10000` cells.  As you build your grid from the `coterm_cty_sf.RDS` file, be sure to reproject the data so that it matches p, and the CRS used in the exercise:

```{r}

```

# Q3

Create a sample variogram for the `AUG` attribute of the precipitation data.  Assume you are *not* worried about outlier observations.

```{r}


```

# Q4

Fit a model variogram to your data.  Justify your choice.

```{r}

```

# Q5

Krige your data using your model variogram.

```{r}


```





